%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
      {\href{https://labsticc.fr/en/directory/tanguy-philippe}{Lab-STICC - ARCAD}} % Organization
      {Cybersecurity Intern - Offensive Tool for Studying SoC Communication Interfaces} % Job title
      {Lorient, France} % Location
      {Apr. 2024 - June 2024} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item[] \hspace{-1em}{Contributed in research and studying the development of offensive tools to analyze System-on-Chip (SoC) communication interfaces using \href{https://github.com/enjoy-digital/litex}{LiteX framework}.: \vspace{0.2em}}
          \item \hspace{1em}{Developed and implemented a System-on-Chip (SoC) on an FPGA board using the LiteX framework.}
          \item \hspace{1em}{Generated SoC using C and Python for SoC definition and configuration.}
          \item \hspace{1em}{Successfully integrated UART, SPI and I2C communication cores on SoC for sniffing purposes.}
          \item \hspace{1em}{Researched comprehensive security assessments and formulated recommendations for enhancements.}
        \end{cvitems}
      }

%---------------------------------------------------------
\vspace{0.3em}

  \cventry
    {\href{https://lambdatheta.com/}{Lambda Theta}} % Organization
    {Design Engineer} % Job title
    {Karachi, Pakistan} % Location
    {Aug. 2022 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] \hspace{-1em}{Constructed test environments/units using UVM and OpenFPGA to create customized FPGA architectures: \vspace{0.2em}}
        \item \hspace{1em}{Utilized Verilog, VHDL, and C++ to develop and test designs, ensuring compatibility across platforms.}
        \item \hspace{1em}{formulated SystemVerilog for testbench creation for the verification of designs.}
        \item \hspace{1em}{Achieved improvements in synthesis and performance through developed prototypes.}
      \end{cvitems}
    }

%---------------------------------------------------------

\vspace{0.3em}

  \cventry
    {\href{https://lambdatheta.com/}{Lambda Theta}} % Organization
    {Computer Vision Intern} % Job title
    {Karachi, Pakistan} % Location
    {July 2021 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[] \hspace{-1em}{Engineered human and object detection algorithms using TensorFlow and OpenCV: \vspace{0.2em}}
        \item \hspace{1em}{Enhanced real-time processing capabilities on RaspberryPi, resulting in detection speed and reliability.}
        \item \hspace{1em}{Integrated an industrial object detection algorithm incorporating volumetric calculations to enhance spatial analysis and efficiency. Integrated the algorithm into a courier company's workflow.}
        \item \hspace{1em}{Systematized extensive testing and validation to ensure robust performance in various environments.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
